### 2019-11-25 thesis.tex
final (?)

% \input{ty}
% \input{epi}

@@

Electrons and ions are sources of electric and magnetic fields. Due to the
long-range nature of these fields, particles can interact simultaneously, at
distance, with several other particles in the system. The effective range of
these interactions is determined by the \emph{Debye length}
\begin{equation}
  \label{debye}
  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
\end{equation}
where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
the plasma density and $e$ the electron charge. This means that a specific
charge will interact effectively only with other charges that are inside of a
virtual sphere with radius given by $\lambda_{De}$, being almost completely
shielded from the influence of particles outside the \emph{Debye sphere}.
The self-consistent interaction between charged particles and electric and
magnetic fields, creates fluctuations in the local neutrality of the plasma,
giving rise to the series of oscillations and complex wave phenomena that
characterize the plasma’s collective behavior~\cite{chen}.

Describing the precise state of a plasma, in a given time, would require
the knowledge of the $6N$ phase-space coordinates of each particle, and also
the microscopic amplitudes of the electric and magnetic fields at each point
in space. Such exact representation is clearly a non-practical approach for
a many-body system like the plasma. However, this microscopic formulation
can be approximated to a macroscopic description by taking the average of
the microscopic quantities and making suitable assumptions to truncate the
correlation functions at an appropriate point~\cite{klimon}. This will lead
to the plasma kinetic equations, which is the first of a hierarchy of
approximations that also includes the multi-fluid and magnetohydrodynamic
theories. The application of each one of these formulations will depend on
the context and the scale of the phenomena being described~\cite{chen}.
In this work we are interested in small-scale processes that depend on
velocity-space properties, requiring a kinetic description of the plasma.

@@

In a first approximation, the plasma dynamics is described by the
Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
\label{boltz}
\end{equation}

@@

It is interesting to mention that at this stage, Eqs. \eqref{form_par}
and \eqref{flut} are precisely the same as those leading to the
quasilinear approximation.
% LFZ180216: Sugiro "are precisely the same as those leading to the
% quasilinear approximation."
% Sabrina: OK
Thus, at this point, one must choose whether the quasilinear approach
is enough, or if a nonlinear formulation is necessary. In the first case
all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
the equation for the fluctuations\footnote{See subsection 3.1.2 of
  \cite{Tigik2015}.}. We shall keep these terms and proceed with the
nonlinear approach.

>>>>

\input{ty}
\input{epi}

@@

Electrons and ions are sources of electric and magnetic fields. Due to the
long-range nature of these fields, particles can interact simultaneously, at
distance, with several other particles in the system. The effective range of
these interactions is determined by the \emph{Debye length}
\begin{equation}
  \label{debye}
  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
\end{equation}
where $T_e$ is the electron temperature\footnote{Due to the high mobility,
  electrons are the main responsible for maintaining the Debye shielding.
  There are specific situations where this is not true~\cite{chen}, but
  they are outside of the scope of the current study.}, $k_B$ the Boltzmann
constant, $n$ the plasma density and $e$ the electron charge. This means
that a specific charge will interact effectively only with other charges
that are inside of a virtual sphere with radius given by $\lambda_{De}$,
being almost completely shielded from the influence of particles outside
the \emph{Debye sphere}. The self-consistent interaction between charged
particles and electric and magnetic fields, creates fluctuations in the
local neutrality of the plasma, giving rise to the series of oscillations
and complex wave phenomena that characterize the plasma’s collective
behavior~\cite{chen}. Describing the precise state of a plasma, in a given
time, requires the knowledge of the $6N$ phase-space coordinates of each
particle, and also the microscopic amplitudes of the electric and magnetic
fields at each point in space~\cite{klimon}. Such exact representation is
clearly a non-practical approach for a many-body system like the plasma.
However, this microscopic formulation can be approximated to a macroscopic
description by taking the average of the microscopic quantities and making
suitable assumptions to truncate the correlation functions at an appropriate
point~\cite{klimon}. This will lead to the plasma kinetic equations, which is
the first of a hierarchy of approximations that also includes the multi-fluid
and magnetohydrodynamic theories. The application of each one of these
formulations will depend on the context and the scale of the phenomena being
described~\cite{chen}. In this work we are interested in small-scale processes
that depend on velocity-space properties, requiring a kinetic description of
the plasma.

@@

Like non-ionized gases, the statistical description of the plasma dynamics
is given by the Boltzmann equation
\begin{equation}
\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
+{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
 +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
\label{boltz}
\end{equation}

@@

It is interesting to mention that at this stage, Eqs. \eqref{form_par}
and \eqref{flut} are precisely the same as those leading to the
quasilinear approximation.
% LFZ180216: Sugiro "are precisely the same as those leading to the
% quasilinear approximation."
% Sabrina: OK
Thus, at this point, one must choose if the quasilinear approach is
enough, or if a nonlinear formulation is necessary. In the first case
all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
the equation for the fluctuations\footnote{See subsection 3.1.2 of
  \cite{Tigik2015}.}. We shall keep these terms and proceed with the
nonlinear approach.
